Probing the Deuteron at Very Large Internal Momenta

### 2020-07-31 MY_PUBLICATIONS/PRL/FINAL_DRAFT/body.tex
updated PRL by including M. Sargsian corections

over the kinematic bin. The

@@

AV18 (green), CD-Bonn (magenta) and WJC2 (orange) NN potentials.}

@@

\noindent systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:

@@

gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.
The data are compared to theoretical calculations using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials. The theoretical calculations

@@

how the NN potential is modeled based on the empirical NN scattering data.

@@

nucleon-meson-meson couplings are constrained to describe the NN scattering phase shifts

@@

which requires comparatively few parameters while still producing a high-precision fit to the NN scattering data.

@@

same NN scattering phase-shifts. The major difference between the CD-Bonn and Paris/AV18/WJC2 

@@

The effects of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.\\

@@

The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)

@@

to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data confirm the Hall A approach of selecting a kinematic

>>>>

@@

AV18 (green), CD-Bonn (magenta) and WJC2 (orange) $NN$ potentials.}

@@

over the kinematic bin. The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:

@@

gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist. The data are compared to theoretical calculations using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} $NN$ potentials. The theoretical calculations

@@

how the $NN$ potential is modeled based on the empirical $NN$ scattering data.

@@

nucleon-meson-meson couplings are constrained to describe the $NN$ scattering phase shifts

@@

which requires comparatively few parameters while still producing a high-precision fit to the $NN$ scattering data.

@@

same $NN$ scattering phase-shifts. The major difference between the CD-Bonn and Paris/AV18/WJC2 

@@

The effects of these local approximations on the $NN$ potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.\\

@@

The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the $NN$ potential where the One Pion Exchange Potential (OPEP)

@@

to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data validates the Hall A approach of selecting a kinematic

### 2020-07-31 MY_PUBLICATIONS/PRL/FINAL_DRAFT/prl.tex
updated PRL by including M. Sargsian corections

%% ****** Start of file template.aps ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.0 of REVTeX, August 2001
%%
%%
%%   Copyright (c) 2001 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
\usepackage{graphicx}  % needed for figures
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\hypersetup{
    colorlinks,
    linkcolor={blue!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}
%

@@

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 05 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by July 31, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\begin{abstract}
  $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  over a range of neutron recoil momenta, $p_{\mathrm{r}}$, with $p_{\mathrm{r}}$ reaching up to $\sim1.0$ GeV/c. The data have
  been obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
  transfer $\vec q$. The new data agree well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar configurations (IC) are suppressed and
  the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
  theoretical calculations, where we observe a significant discrepancy for missing momenta $p_{\mathrm{r}}>700$ MeV/c. 
\end{abstract}

>>>>

%% ****** Start of file template.aps ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.0 of REVTeX, August 2001
%%
%%
%%   Copyright (c) 2001 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
\usepackage{graphicx}  % needed for figures
\usepackage{ragged2e}
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\hypersetup{
    colorlinks,
    linkcolor={blue!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}
%

@@

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 06 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by July 31, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\begin{abstract}
  $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  over a range of neutron recoil momenta, $p_{\mathrm{r}}$,  reaching up to $\sim1.0$ GeV/c. The data were
  obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
  transfer $\vec q$. The new data agree well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar currents (IC) are suppressed and
  the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
  theoretical calculations, where we observe a significant discrepancy for missing momenta $p_{\mathrm{r}}>700$ MeV/c. 
\end{abstract}
